\documentclass{ansjournal}

\usepackage{microtype}                     % Improve typography
\usepackage{amsmath, mathtools}             % AMS Math extensions
\usepackage{booktabs}                      % Improved table spacing
\usepackage{siunitx}
\usepackage{breqn}
\usepackage{nicefrac}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{dblfloatfix}
\usepackage{color}
\usepackage{todonotes}
\usepackage{etoolbox}
\usepackage{listings}
\usepackage{color}
\usepackage{bbold}
\usepackage{breqn}
\usepackage{xcolor}

% Checkmarks
\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\newcommand{\code}[2]{
  \subsection*{#1}
  \lstinputlisting{#2}
}

\lstset{
  basicstyle=\footnotesize\ttfamily,
  columns=fullflexible,
  showstringspaces=false,
  commentstyle=\color{gray}\upshape,
  frame=single,
  xleftmargin=0.8in,
  xrightmargin=0.8in
}

\crefname{lstlisting}{Listing}{Listings}

% Patch to make equation autoref counter work
\makeatletter
\patchcmd\eq@setnumber{\stepcounter}{\refstepcounter}{}{%
  \errmessage{Patching \noexpand\eq@setnumber failed}%
}
\makeatother

\hypersetup{colorlinks=true,
  pdftitle={Multigroup Cross-Section Generation with the OpenMC Monte Carlo Particle Transport Code},
  pdfauthor={William Boyd, Adam Nelson, Paul Romano, Samuel Shaner, Benoit Forget and Kord Smith}}

\title{Multigroup Cross-Section Generation with the OpenMC Monte Carlo Particle Transport Code}

\author[a]{William Boyd\footnote{Email: \href{mailto:wboyd@mitre.org}{wboyd@mitre.org}}\footnote{This author was a graduate research assistant at the Massachusetts Institute of Technology at the time this research was conducted. The author's affiliation with The MITRE Corporation is provided for identification purposes only, and is not intended to convey or imply MITRE's concurrence with, or support for, the positions, opinions or viewpoints expressed by the author. Approved for Public Release and Distribution Unlimited Case 18-2679.}}
\author[b]{Adam Nelson}
\author[c]{Paul K. Romano}
\author[d]{Samuel Shaner}
\author[d]{Benoit Forget}
\author[d]{Kord Smith}

\affil[a]{MITRE Corporation, 7525 Colshire Drive, McLean, Virginia 22102}
\affil[b]{Naval Reactors, 1240 Isaac Hull Ave. SE, Washington Navy Yard, D.C. 20376}
\affil[c]{Argonne National Laboratory, Mathematics and Computer Science
  Division, 9700 South Cass Avenue, Lemont, Illinois 60439}
\affil[d]{Massachusetts Institute of Technology, Department of Nuclear Science
  and Engineering, 77 Massachusetts Avenue, Building 24, Cambridge,
  Massachusetts 02139}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abstractText{High-fidelity deterministic transport codes require highly accurate multigroup cross sections (MGXS). Monte Carlo is increasingly cited as a reactor-agnostic approach to MGXS generation since it is unconstrained by the engineering-based approximations that limit the applicability of deterministic MGXS generation tools. This paper introduces a new framework that uses the OpenMC Monte Carlo code to generate MGXS for use in multigroup transport codes. The \texttt{openmc.mgxs} module is built atop OpenMC's Python API to process tally data output by the OpenMC executable. This paper validates the module to generate MGXS that enable the multigroup OpenMOC transport code to compute eigenvalues to within 50 pcm and fission rates to within 1\% of reference solutions for two heterogeneous pressurized water reactor benchmarks.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\keywordsText{Monte Carlo neutron transport, multigroup cross-section generation, OpenMC}

\begin{document}

\maketitle

\input{introduction}
\input{mg-methods}
\input{mgxs-mc}
\input{openmc}
\input{design}
\input{results}
\input{conclusions}
\input{acknowledgements}

%\section*{References}
\setlength{\baselineskip}{12pt}
\bibliography{references}
\bibliographystyle{ans}

\end{document}
